nmds-plots

### 2023-02-13 workflow/notebooks/nmds-plots.Rmd
updated file reading to use here library

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("vegan")
# install.packages("readr")
```

```{r prepdata, include=FALSE}
library(vegan)
library(readr)
library(tidyverse)
library(ggplot2)
# source(here::here("code","plot","config-plots.R"))
# pc = read_tsv(here("data", "mothur", "cdi.opti_mcc.braycurtis.0.03.lt.ave.nmds.axes")
pc = read_tsv("/Users/megan/Desktop/schloss-lab/adverseCDI/data/mothur/cdi.opti_mcc.braycurtis.0.03.lt.ave.nmds.axes")
case_data <- read.csv("/Users/megan/Desktop/schloss-lab/adverseCDI/data/process/cases_full_metadata.csv")
 #make community matrix - extract columns with abundance information
# com = pc[,2:ncol(pc)] 
  #turn abundance data frame into a matrix
# m_com = as.matrix(com)
# set.seed(123)
# minShift <- function(x) {x + abs(min(x))}
# m_com <- apply(m_com, 2, minShift)
# nmds = metaMDS(m_com, distance = "bray")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("vegan")
# install.packages("readr")
library(vegan)
library(readr)
library(tidyverse)
library(ggplot2)
library(data.table)
library(here)
```

```{r prepdata, include=FALSE}
# source(here::here("code","plot","config-plots.R"))
# pc = read_tsv(here("data", "mothur", "cdi.opti_mcc.braycurtis.0.03.lt.ave.nmds.axes")
# pc = read_tsv("/Users/megan/Desktop/schloss-lab/adverseCDI/data/mothur/cdi.opti_mcc.braycurtis.0.03.lt.ave.nmds.axes")
pc <- data.table::fread(here('data', 'mothur',
                                      'cdi.opti_mcc.braycurtis.0.03.lt.ave.nmds.axes'))
#case_data <- read.csv("/Users/megan/Desktop/schloss-lab/adverseCDI/data/process/cases_full_metadata.csv")
case_data <- data.table::fread(here('data', 'process',
                                      'cases_full_metadata.csv'))
```
